Quality Definitions of Qualities

### 2019-12-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updates to quality definitions document - added mostly ISI 9126 definitions

\begin{defn}
  The capability of a software product to be installed in a specified
  environment \citep{iso2001iec}. (As summarized in
  \citep{berander2005software}.)  \wss{remove the quotation marks - we are
    assuming all definitions are directly quoted from the source. Please remove
    quotes for all of the definitions that you ``own.''}  \oo{Done}
\end{defn}

@@

@@

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  \citep{iso2001iec}. (As summarized in \citet{berander2005software}.)
\end{defn}

@@

\begin{defn} \label{reliabilitySelected2}
   Reliability expresses the ability of the software to maintain a specified
   level of fault tolerance, when used under specified condition \citep{singh2013different}.
\end{defn}
\begin{defn}
	The extent to which a program can be expected to perform its intended
	function with required precision \citep{McCallEtAl1977}. (As summarized in
    \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  The ability of a system or component to to perform its required function under
  stated conditions for a specified period of time
  \citep{IEEEComputerDictionary1991}
\end{defn}

@@

Reliability is defined in a way that the measurement metrics are visible - the
specified enviroment, the specified time and the specified level of fault
tolerance. Reliability is a critical quality for scientific software, since the
results of computations are meaningless, if they are not dependable.
Reliability is closely tied to verifiability, since the key quality to verify is
reliability, while the act of verification itself improves reliability.

@@

@@

@@

\subsection{\notdone{Portability} \pmi{owner}}
\begin{defn}
  The ease with which a system or component can be transferred from one hardware
  or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  An application is portable across a class of environments to the degree that
  the effort required to transport and adapt it to a new environment in the
  class is less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected} 
  Effort required to transfer the program from one hardware and/or software
  system environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
  A set of attributes that bear on the ability of software to be transferred
  from one environment to another (including the organizational, hardware, of
  software environment) \citep{pfleeger2006software}.
\end{defn}
\begin{defn}
  Code possesses the characteristic of portability to the extent that it can be
  operated easily and well on computer configurations other than its current
  one. This implies that special function features, not easily available at
  other facilities, are not used, that standard library functions and
  subroutines are selected for universal applicability, and so on
  \citep{boehm2007software}.
\end{defn}
\begin{defn}
  Portability refers to the ability to run a system on different hardware
  platforms \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
	``The effort required to transfer a program from one hardware and/or software
	environment to another'' \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.)
\end{defn}

@@

@@

@@

@@

@@

24765-2017 - ISO/IEC/IEEE International Standard - Systems and software
engineering--Vocabulary
has a full definition, namely
\begin{enumerate}
\item the degree to which a relationship can be established between two or more
  products of the development process, especially products having a
  predecessor-successor or master-subordinate relationship to one another;
\item the identification and documentation of derivation paths (upward) and
  allocation or flowdown paths (downward) of work products in the work product
  hierarchy;
\item the degree to which each element in a software development product
  establishes its reason for existing; and discernible association among two or
  more logical entities, such as requirements, system elements, verifications,
  or tasks.
\end{enumerate}

>>>>

\begin{defn}
  The capability of a software product to be installed in a specified
  environment \citep{ISO9126}. (As summarized in
  \citep{berander2005software}.)  \wss{remove the quotation marks - we are
    assuming all definitions are directly quoted from the source. Please remove
    quotes for all of the definitions that you ``own.''}  \oo{Done} \wss{I've
    verified that this definition is correct.  We do not have to cite the
    textbook anymore, since we have the original source.}
\end{defn}

@@

\begin{defn}
Testability is the capability of the software product to enable modified
software to be validated \cite{ISO9126}.
\end{defn}

@@

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  \citep{iso2001iec}. (As summarized in \citet{berander2005software}.)
  \wss{This definition does not match the definition I found in the
    \cite{ISO9126}.  @olu, can you please look into this?  My definition is
    given below.  Also, I've added a pdf of the ISO standard to the pub repo.}
\end{defn}

@@

\begin{defn} \label{reliabilitySelected2} 
  Reliability expresses the ability of the software to maintain a specified
  level of fault tolerance, when used under specified condition
  \citep{singh2013different}.
\end{defn}

\begin{defn}
  The extent to which a program can be expected to perform its intended function
  with required precision \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.) \wss{When we have a copy of the McCall reference we can
    verify this and simply cite the primary source.}
\end{defn}

@@

\begin{defn}
  The ability of a system or component to perform its required function under
  stated conditions for a specified period of time
  \citep{IEEEComputerDictionary1991}
\end{defn}

\begin{defn}
 The capability of the software to maintain the level of performance of the
 system when used under specified conditions \cite{ISO9126}.
\end{defn}

@@

Reliability is defined in a way that the measurement metrics are visible - the
specified environment, the specified time and the specified level of fault
tolerance. Reliability is a critical quality for scientific software, since the
results of computations are meaningless, if they are not dependable.
Reliability is closely tied to verifiability, since the key quality to verify is
reliability, while the act of verification itself improves reliability.

@@

\begin{defn}
  The capability of the software to be understood, learned, used and liked by
  the user, when used under specified conditions \cite{ISO9126}.
\end{defn}
\noindent \textbf{Proposed Definition}

@@

\begin{defn}
  The capability of the software to be modified.  Modifications may include
  corrections, improvements or adaptation of the software to changes in
  environment, and in requirements and functional specifications. \cite{ISO9126}
\end{defn}

@@

\subsection{\notdone{Portability} \pmi{owner}}

\begin{defn}
  The ease with which a system or component can be transferred from one hardware
  or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}

\begin{defn}
  An application is portable across a class of environments to the degree that
  the effort required to transport and adapt it to a new environment in the
  class is less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}

\begin{defn} \label{PortabilityDefnSelected} 
  Effort required to transfer the program from one hardware and/or software
  system environment to another \citep{pressman2005software}.
\end{defn}

\begin{defn}
  A set of attributes that bear on the ability of software to be transferred
  from one environment to another (including the organizational, hardware, of
  software environment) \citep{pfleeger2006software}.
\end{defn}

\begin{defn}
  Code possesses the characteristic of portability to the extent that it can be
  operated easily and well on computer configurations other than its current
  one. This implies that special function features, not easily available at
  other facilities, are not used, that standard library functions and
  subroutines are selected for universal applicability, and so on
  \citep{boehm2007software}.
\end{defn}

\begin{defn}
  Portability refers to the ability to run a system on different hardware
  platforms \citep{ghezzi1991fundamentals}.
\end{defn}

\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

\begin{defn}
  The capability of software to be transferred from one environment to another
  \cite{ISO9126}.
\end{defn}
\noindent \textbf{Proposed Definition}

@@

\begin{defn}
  The capability of the software product to enable the user to understand
  whether the software is suitable, and how it can be used for particular tasks
  and conditions of use \cite{ISO9126}.
\end{defn}

@@

\begin{defn}
  The capability of the software to interact with one or more specified systems
  \cite{ISO9126}.
\end{defn}
\noindent \textbf{Proposed Definition}

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

24765-2017 - ISO/IEC/IEEE International Standard - Systems and software
engineering--Vocabulary
has a full definition, namely
\begin{enumerate}
\item the degree to which a relationship can be established between two or more
  products of the development process, especially products having a
  predecessor-successor or master-subordinate relationship to one another;
\item the identification and documentation of derivation paths (upward) and
  allocation or flow-down paths (downward) of work products in the work product
  hierarchy;
\item the degree to which each element in a software development product
  establishes its reason for existing; and discernible association among two or
  more logical entities, such as requirements, system elements, verifications,
  or tasks.
\end{enumerate}

\begin{defn}
  The ability to link software components to requirements
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}
